The Rockerverse: Images, Packages, and Applications for Containerization with R

### 2020-01-22 manuscript.Rmd

@@

The ordering of authors following DN as first author is alphabetical.
DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DB wrote the section on \pkg{outsider}.
GD contributed the CARD.com use case.
DE wrote the introduction and the section about Containerization and Rocker.
RC \& EH contributed to the section on interfaces for Docker in R.
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
BM wrote the section on research compendia and made the project Binder-ready.
HN \& JN co-wrote the section on enterprise production environments (\pkg{googleComputeEngineR}, Google Cloud Run, Kubernetes).
KR wrote the section about \pkg{wholepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
NX wrote the section on \pkg{liftr}.
All authors approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.

>>>>

**Whole Tale** (https://wholetale.org) is a National Science Foundation (NSF) funded project developing a scalable, open-source, multi-user platform for reproducible research \citep{brinckman2019, chard2019a}.
A central goal of the platform is to enable researchers to easily create and publish executable research objects\footnote{In Whole Tale a `tale` is a research object that contains metadata, data (by copy or reference), code, narrative, documentation, provenance, and information about the computational environment to support computational reproducibility} associated with published research \citep{chard2019b}.
For R users, Whole Tale attempts to combine the strengths of the Rocker Project's curated Docker images with the Jupyter Project's `repo2docker`\footnote{See \href{https://repo2docker.readthedocs.io/}{https://repo2docker.readthedocs.io/}} component to simplify the customization of R-based environments for researchers with limited experience with either Docker or Git.
Using Whole Tale, researchers can create and publish Rocker-based reproducible research objects to a growing number of repositories including DataONE member nodes, Zenodo and soon Dataverse.
Additionally, Whole Tale supports automatic data citation and is working on capabilities for image preservation and provenance capture to improve the transparency of published computational research artifacts \citep{mecum2018, mcphillips2019}.
Multiple options have been discussed to allow users to change the base image used in `repo2docker` from the default Ubuntu LTS required to support the Rocker Project images. 
Whole Tale implemented a custom `RockerBuildPack`\footnote{See \href{https://github.com/whole-tale/repo2docker\_wholetale}{https://github.com/whole-tale/repo2docker\_wholetale}} to support customization of the `rocker/geospatial` image through `repo2docker` composability \footnote{Composability refers to the ability to combine multiple package managers -- such as R, `pip`, and `conda`}.
This works in part because Rocker images are based on a Debian distribution.

@@

The ordering of authors following DN as first author is alphabetical.
DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DB wrote the section on \pkg{outsider}.
GD contributed the CARD.com use case.
DE wrote the introduction and the section about Containerization and Rocker.
RC \& EH contributed to the section on interfaces for Docker in R.
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
BM wrote the section on research compendia and made the project Binder-ready.
HN \& JN co-wrote the section on enterprise production environments (\pkg{googleComputeEngineR}, Google Cloud Run, Kubernetes).
KR wrote the section about \pkg{wholepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
CW wrote the sections on Whole Tale and contributed the publication reproducibility audit use case.
NX wrote the section on \pkg{liftr}.
All authors approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.
